\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

It’s been two years since I started this journey. It has been an interesting apprenticeship not only in the scientific and academic fields but in the professional and personal ones. Achieving this goal means a lot to me and I want to thank everyone that has supported and helped me during the process. However, there are a couple of individuals who deserve special mention.

Firstly, I would like to thank God 

I also want to thank my advisor \textbf{\myProfFirstName} \textbf{\myProfLastName} for ... \hinttext{well, you should know why. You supervisors are definitely going to read this. What exceptional traits of them helped you to further your research or were there memorable moments during your candidature that you would like them to recall?}

 my co-supervisor \textbf{\myOtherProfTitle} \textbf{\myOtherProfFirstName} \textbf{\myOtherProfLastName} for ... \hinttext{well, you should know why. You supervisors are definitely going to read this. What exceptional traits of them helped you to further your research or were there memorable moments during your candidature that you would like them to recall?}

Furthermore, I also want to thank all the members of the \emph{La Trobe student society / club / research group} \hinttext{(whichever applies)} for the many discussions and valuable inputs along the way. A special thanks goes to \textbf{Proofreader's name} for helping me improve my English grammar \hinttext{(if English is not your mother tongue you should get your thesis checked!)}; \textbf{Name of individual or organization that supported you} for ... \hinttext{(try to sum up in one sentence what they did to aid your research, personal development, etc.)}; and \textbf{Author who wrote letter of support no.~1}, \textbf{Author who wrote letter of support no.~2} and \textbf{Name of the research coordinator at the time} for their support of my scholarship application, without which my candidature would not have been possible.

I also want to thank my wife/husband/partner \textbf{Spouse's name}, who took care of our son/daughter/kids during the many days and nights that I spent at the university and made sure that I had a comfy home to go back to every day. And of course\textemdash{}last but not least\textemdash{}I want to thank my son/daughter/kids \textbf{Child Name 1}, \textbf{Child name 2} and \textbf{Child name 3} for \hinttext{... well, you should know why!}

